Localisation and Sensor Privacy Using the Extended Information Filter and Private Linear-Combination Aggregation\thanksref{footnoteinfo}

### 2020-10-05 main.tex
Added reference for the recommended keysize for our scheme

In addition to accuracy, computational requirements are an important factor in the adoption of novel cryptographic methods. Figure \ref{fig:sim_timing} shows the average simulation runtimes when encryption key bit lengths (\textit{i.e.} bit lengths of $N$) and the number of sensors are varied. Every plotted time is again the average of $100$ simulations, each running for $50$ filter iterations. 
\begin{figure}[htbp]
\begin{center}
    \includegraphics{images/timing.pdf}
\end{center}
\caption{Timing}
\label{fig:sim_timing}
\end{figure}
As sensor and navigator computations run in parallel, increases in runtime from additional sensors are primarily due to the longer aggregation operation at the navigator. The predominant computational cost is dependant on the encryption scheme key size, which must be chosen such that sufficient security is provided by the scheme. The current recommendation for a secure implementation of the Paillier encryption scheme is to use $1024$ bit-long keys.

>>>>

In addition to accuracy, computational requirements are an important factor in the adoption of novel cryptographic methods. Figure \ref{fig:sim_timing} shows the average simulation runtimes when encryption key bit lengths (\textit{i.e.} bit lengths of $N$) and the number of sensors are varied. Every plotted time is again the average of $100$ simulations, each running for $50$ filter iterations. 
\begin{figure}[htbp]
\begin{center}
    \includegraphics{images/timing.pdf}
\end{center}
\caption{Timing}
\label{fig:sim_timing}
\end{figure}
As sensor and navigator computations run in parallel, increases in runtime from additional sensors are primarily due to the longer aggregation operation at the navigator. The predominant computational cost is dependant on the encryption scheme key size, which must be chosen such that sufficient security is provided by the scheme. The current recommendation for a secure implementation relying on prime factorisation (difficulty of factorising $N$) is to use $2048$ bit-long keys \cite{barkerRecommendationPairwiseKey2019}.
